Supplementary Information

### 2021-08-31 doc/manuscript/ForestGEO_treerings.Rmd

year_trends_all_legend= "Figure S16. Responses of annual growth, expressed as ring width (RW), (b) basal area increment (BAI), or (c) aboveground biomass (AGB) increase, to calendar year for 35 species at 10 sites."
```

>>>>

year_trends_all_legend= "Figure S16. Responses of annual growth, expressed as ring width (RW), (b) basal area increment (BAI), or (c) aboveground biomass (AGB) increase, to calendar year for 35 tree species at 10 sites."
```
